\huge Tor's Usability for Censorship Circumvention

### 2016-04-08 pets2017-paper/pets2017-paper.tex
Move a \label after a \caption.
This is needed for cross-references to work right; otherwise the \label
will refer to the previous labelable thing in the text.
Caption for the topology graphic I want to add.
Maybe this should just be inline, not a floating figure.

\subsection{Interacting Network Components} 
For context, we define bridges, pluggable transports, and proxies, network components that 
circumvent censorship and interact with the Tor configuration interface. 
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

@@

\begin{figure*}[t]
	\label{fig:old-flow}
	\centering
		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
		\caption{old flow} 
\end{figure*}

>>>>

\subsection{Interacting Network Components} 
For context, we define bridges, pluggable transports, and proxies, network components that 
circumvent censorship and interact with the Tor configuration interface. 
These components are shown in Fig.~\ref{fig:topology}.
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

\begin{figure}
\centering
{\color{red} TODO}
% \includegraphics{topology}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
		\caption{old flow} 
	\label{fig:old-flow}
\end{figure*}
